\vspace{-1in}Identity signaling model progress

### 2020-02-26 reports/Progress-2-25.tex
complete prototype of minorities experiment

\section*{Evolution in signaling strategy}

For these preliminary results I focus on the evolution of signaling strategies,
and set receiving strategies to be randomly assigned with probability 0.5 to
each agent at model initialization. The output measure in these experiments
is density of covert signalers. There are confirmatory results for two
computational experiments in which I: (1) varied relative covert receptivity $r/R$ and 
homophily, $w$; and (2) varied the disliking penalties set equal, $d=\delta$,
and homophily, $w$.

\subsection*{Density of covert signalers vs. $r/R$ and homophily, $w$}

@@

\subsection*{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}

Here we co-vary the disliking penalties, which we set equal ($d=\delta$), and
homophily, $w$. I ran the model to 200 timesteps this time, which did allow
the series to settle more, but perhaps not to a significant degree 
(Figure~\ref{fig:dislikingHomophilySeries}). The bonus payoff for two 
interacting agents where at least one
likes the other is set fixed to $s=0.25$. The payoff structure is as follows

\begin{table}[H]
  \centering
  \begin{tabular}{rl}
   Attitude combo. & Payoff \\
   \toprule
    Like/like & $1 + s$ \\
    Like/neutral & $1 + s$ \\
    Neutral/neutral & 1 \\
    Like/dislike & $1 + s - d$ \\
    Dislike/neutral & $1 - d$ \\
    Dislike/dislike & $1 - d - \delta$
  \end{tabular}
\end{table}

Specifically, we vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
As in the above experiment, we set $w \in \{0.0, 0.5, \ldots, 0.45\}$.

@@

\section*{Discussion}

These preliminary experiments and results are based on one major finding from
ECS that covert signaling is maintained when overt signalers do not have
too large an advantage in the free choice context. ``This requires that
assortment with liked individuals not be too accurate,'' which corresponds to
small $w$ in this ABM version. ``The accuracy of assortment is influenced
by the reception probabilities of both signal types, $R$ and $r$'' (see p.
4 in ECS). Our preliminary results find the same trend with our ABM.

>>>>

\section{Evolution in signaling and receiving strategies}

For these preliminary results I focus on the evolution of signaling strategies,
each agent at model initialization. There are two output measures in these experiments:
density of covert signalers and density of churlish receivers. 
There are confirmatory results for two computational experiments in which I: 
(1) varied relative covert receptivity $r/R$ and 
homophily, $w$; and (2) varied the disliking penalties set equal, $d=\delta$,
and homophily, $w$.

The bonus payoff for two 
interacting agents where at least one
likes the other is set fixed to $s=0.25$. The payoff structure is as follows

\begin{table}[H]
  \centering
  \begin{tabular}{rcc}
    Attitude combo. & Payoff (similar) & Payoff (dissim.) \\
   \toprule
    Like/like & $1 + s$                    & NA \\
    Like/neutral & $1 + s$                 & NA \\
    Like/dislike & $1 + s - d$             & NA \\
    Neutral/neutral & 1 + s                & 1  \\
    Dislike/neutral & $1 + s - d$          & $1-d$\\
    Dislike/dislike & $1 + s - d - \delta$ & $1 - d - \delta$
  \end{tabular}
\end{table}

Agents only interact with one another with probability given by their attitudes
towards one another. If two agents are assorted together to potentially 
interact, these are the probabilities the agents do interact.

\begin{table}[H]
  \centering
  \begin{tabular}{rc}
    Attitudes & Pr(paired agents interact) \\
    \toprule
    Like/like & $0.5 + w$ \\
    Like/neutral & $0.5 + \frac{w}{2}$ \\
    Like/dislike & $0.5$ \\
    Neutral/neutral & $0.5$ \\
    Dislike/neutral & $0.5 - \frac{w}{2}$ \\
    Dislike/dislike & $0.5 - w$ 
  \end{tabular}
\end{table}

\subsection{Density of covert signalers vs. $r/R$ and homophily, $w$}

@@

\subsection{Density of covert signalers vs. disliking penalty $d=\delta$ and homophily, $w$}

Here I co-vary the disliking penalties, which I set equal ($d=\delta$), and
homophily, $w$. Here, $r=0.25$ and $R=0.5$.

Specifically, I vary $d=\delta \in \{0.0, 0.05, 0.1, \ldots, 0.45\}$
As in the above experiment, I set $w \in \{0.0, 0.5, \ldots, 0.45\}$.

@@

\subsection{Correlations between proportion of covert signalers and of churlish receivers}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/receptivity_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/disliking_allcombos_reg.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Correlation between proportion of covert signalers and proportion of
    churlish receivers for all tested parameter combinations in both 
    receptivity (a) and disliking (b) experiments.}
  \label{fig:regressions}
\end{figure}

\section{Minority populations}

So far in these results I tested the case where a 10\% of all agents have
the minority trait, $+1$ in the first trait vector position. 
The other 90\% have the majority trait, $-1$ in the first trait vector position.

$r=0.25$, $R=0.5$.

\subsection{Covert signaling}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_majority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_minority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of covert signaling in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_signalers.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_signalers.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of covert signalers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff.pdf}
  \caption{Difference between proportion of covert signalers in the minority 
    and majority populations. When cost of disliking is high and homophily is 
    low, more minority agents are covert signalers than majority agents,
    proportionally. An increase in homophily enables minority agents to 
    find one another more easily, so overt signaling, which reaches more of
    the population, is advantageous.
  }
  \label{fig:}
\end{figure}

\subsection{Churlish receiving}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_majority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_minority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of churlish receiving in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_receivers.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_receivers.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of churlish receivers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff.pdf}
  \caption{Difference between proportion of churlish receivers in the minority 
    and majority populations. Here the dependence is primarily on homophily.
    If homophily is too low, the minority population cannot interact often
    enough with their in-group, and so must adopt a non-churlish stance towards
    others in order to not suffer cost of disliking penalties. Once the minority
    can reliably find its in-group members (increasing homophily) the minority
    can afford to assume they dislike others, since by and large they dislike
    the majority.
  }
  \label{fig:}
\end{figure}

% \section{Discussion}

% These preliminary experiments and results are based on one major finding from
% ECS that covert signaling is maintained when overt signalers do not have
% too large an advantage in the free choice context. ``This requires that
% assortment with liked individuals not be too accurate,'' which corresponds to
% small $w$ in this ABM version. ``The accuracy of assortment is influenced
% by the reception probabilities of both signal types, $R$ and $r$'' (see p.
% 4 in ECS). Our preliminary results find the same trend with our ABM.
